Visualizing probability distributions across bivariate cyclic temporal granularities

### 2020-02-10 main.Rmd
cricketdata change -  with lag dot and wicket

  #filter(fielding_wckts %in% c(0,1)) %>% 
  cricket_data %>% prob_plot("over","lag_field",
                               hierarchy_model,
                               response = "run_rate",
                               plot_type = "violin",
                               quantile_prob = c(0.1, 0.25, 0.5, 0.75, 0.9),
           overlay = TRUE)  + ggtitle("") + geom_boxplot(width = 0.5)
```

>>>>

  #filter(fielding_wckts %in% c(0,1)) %>% 
  cricket_data %>% prob_plot("over","lag_field",
                               hierarchy_model,
                               response = "run_rate",
                               plot_type = "violin",
                               quantile_prob = c(0.1, 0.25, 0.5, 0.75, 0.9))  + ggtitle("") + geom_boxplot(width = 0.5)
```
